Early Warning Signals and the Prosecutor's Fallacy

### 2014-11-20 comment-reply-code/comment.Rmd
rename

`ro warning=FALSE, message=FALSE, comment=NA, tidy=FALSE, cache=TRUE, verbose=TRUE, cache.path="figure2/" or`

# Code for Prosecutors Fallacy

@@

``` {r libraries}
library(populationdynamics)
library(earlywarning)
library(reshape2)		# data manipulation
library(data.table)	# data manipulation
library(ggplot2)		# graphics
library(snowfall)		# parallel
````

@@

Then we fix a set of paramaters we will use for the simulation function.  Since we will simulate 20,000 replicates with 50,000 pts a piece, we can save memory by performing the conditional selection on the ones that crash as we go along and disgard the others.  (We will create a null distribution in which we ignore this conditional selection later).

``` {r simdatf}
threshold <- 250
select_crashes <- function(n){
	T<- 5000
	n_pts <- n
	pars = c(Xo = 500, e = 0.5, a = 180, K = 1000, h = 200,
    i = 0, Da = 0, Dt = 0, p = 2)
	sn <- saddle_node_ibm(pars, times=seq(0,T, length=n_pts), reps=1000)
	d <- dim(sn$x1)
	crashed <- which(sn$x1[d[1],]==0)
	sn$x1[,crashed] 
}
````

To take advantage of parallelization, we loop over this function a set number of times.  The `snowfall` library provides the parallelization
of the `lapply` loop.  A few extra commands format the data into a table
with columns of times, replicate id number, and population value at the
given time.

@@

``` {r subsetdata, dependson="simdat" }
require(plyr)
zoom <- ddply(dat, "reps", function(X){
    tip <- min(which(X$value<threshold))
#print(tip)
    index <- max(tip-200,1):tip
    data.frame(time=X$time[index], value=X$value[index])
    })
save(zoom, file="zoom.rda")
````

@@

``` {r fig2, dependson="nullmelt"}
ggplot(dat) + geom_histogram(aes(value, y=..density..), binwidth=0.3, alpha=.5) +
 facet_wrap(~variable) + xlim(c(-1, 1)) + 
 geom_density(data=nulldat, aes(value), adjust=2) + xlab("Kendall's tau") + theme_bw()

@@

``` {r figure2, dev="CairoPS", fig.ext="eps", fig.width=6, fig.height=5, include=FALSE}
ggplot(dat) + geom_histogram(aes(value, y=..density..), binwidth=0.3, alpha=.5) +
 facet_wrap(~variable) + xlim(c(-1, 1)) + 
 geom_density(data=nulldat, aes(value), adjust=2) + xlab("Kendall's tau") + theme_bw()

@@

``` {r save_final_data}
write.csv(dat, file="Figure2_dat.csv")
write.csv(nulldat, file="Figure2_nulldat.csv")
```

>>>>

``` {r libraries}
rm(list=ls())
library(earlywarning)
library(reshape2)		# data manipulation
library(data.table)	# data manipulation
library(ggplot2)		# graphics
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA, tidy=FALSE, verbose=TRUE, cache=FALSE)
````

@@

``` {r libs}
library(populationdynamics)
library(snowfall)   # parallel
````

@@

Then we fix a set of paramaters we will use for the simulation function.  Since we will simulate 20,000 replicates with 50,000 pts a piece, we can save memory by performing the conditional selection on the ones that cross a threshold we go along and disgard the others.  (We will create a null distribution in which we ignore this conditional selection later).

``` {r simdatf}
threshold <- 250
select_crashes <- function(n){
  T<- 5000
  n_pts <- n
  pars = c(Xo = 500, e = 0.5, a = 180, K = 1000, h = 200,
    i = 0, Da = 0, Dt = 0, p = 2)
  sn <- saddle_node_ibm(pars, times=seq(0,T, length=n_pts), reps=1000)
  d <- dim(sn$x1)
  crashed <- which(sn$x1[d[1],] <= threshold)
# crashed <- which(sn$x1[d[1],]==0)
  sn$x1[,crashed] 
}
````

 A few extra commands format the data into a table
with columns of times, replicate id number, and population value at the
given time.

@@

``` {r subsetdata, dependson="simdat" }
require(plyr)
zoom <- ddply(dat, "reps", function(X){
    tip <- min(which(X$value<threshold))
    index <- max(tip-200,1):tip
    data.frame(time=X$time[index], value=X$value[index])
    })
````

@@

``` {r fig, dependson="nullmelt"}
ggplot(dat) + geom_histogram(aes(value, y=..density..), binwidth=0.3, alpha=.5) +
 facet_wrap(~variable) + xlim(c(-1, 1)) + 
 geom_density(data=nulldat, aes(value), adjust=2) + xlab("Kendall's tau") + theme_bw()

@@

``` {r save_final_data}
write.csv(dat, file="allee.csv")
write.csv(nulldat, file="allee_nulldat.csv")
```

``` {r comment, dev="CairoPS", fig.ext="eps", fig.width=6, fig.height=5, include=FALSE}
ggplot(dat) + geom_histogram(aes(value, y=..density..), binwidth=0.3, alpha=.5) +
 facet_wrap(~variable) + xlim(c(-1, 1)) + 
 geom_density(data=nulldat, aes(value), adjust=2) + xlab("Kendall's tau") + theme_bw()

@@

### 2014-11-20 doc/no-signals-for-stochastic-transitions/sig-tests.Rmd
rename

There should be some clever way in plyr or data.table to do these combinations automatically, but anyway:

Focusing on the OU model, we see that autocorrelation is not sufficiently different:

>>>>

(there should be some clever way in plyr or data.table to do these combinations automatically, but anyway)

Focusing on the OU model, we do see some 'significant' difference in autocorrelation distributions:
